Reviewer comments from PeerJ

### 2015-03-23 Supplement_mbh.tex
edits to supplement

% Appendix S3. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=180mm]{FigS1LocusCartoon.png}
   \flushleft{Figure S1: Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Region 1; within the 5' UTR, and Region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

% Appendix S4. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2GelPeerJ.png}
   \flushleft{Figure S2: Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

% Appendix S5. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.png}
    \flushleft{Figure S3: Neighbor-joining tree of the sequenced region in the 5' UTR (right; Region 1) and the 66,169 bp upstream region (left; Region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion. EjuA refers to individuals from population Ejutla A, EjuB from Ejutla B, SLO from San Lorenzo, and MSA from La Mesa. Remaining individuals are lines of maize (\emph{Zea mays} ssp. \emph{mays}).}

>>>>

% Appendix S3. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
%\begin{figure*}[!t]
  %\begin{center}
   %\includegraphics[width=180mm]{FigS1LocusCartoon.png}
   %\flushleft{Figure S1: Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Region 1; within the 5' UTR, and Region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  %\end{center}
%\end{figure*}
%-------------------------------------------------------------------

@@

% Appendix S4. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2GelPeerJ_pretty.png}
   \flushleft{Figure S1: Agarose gel image of amplification products for genotyping of the \emph{Hopscotch} element. Lanes 1 (HopF/HopR; 5kb band) and 2 (HopF/HopIntR; 1.1kb) are the products for one individual that is homozygous for the element; Lanes 3 (HopF/HopR; 5kb band) and 4 (HopF/HopIntR; 1.1kb) are also the products of an individual that is homozygous for the element; and Lanes 5 (HopF/HopR; 300bp) and 6 (HopF/HopIntR; N/A) are the products of an individual that is homozygous for the teosinte (lacking the \emph{Hopscotch}) allele.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

% Appendix S5. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=150mm]{FigS3NJtrees.png}
    \flushleft{Figure S2: Neighbor-joining tree of the sequenced region in the 5' UTR (right; Region 1) and the 66,169 bp upstream region (left; Region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion. EjuA refers to individuals from population Ejutla A, EjuB from Ejutla B, SLO from San Lorenzo, and MSA from La Mesa. Remaining individuals are lines of maize (\emph{Zea mays} ssp. \emph{mays}).}
